Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV

### 2017-11-23 paper.tex
adding ack
removed comment-out
remove convert
recommit
into svn
final to PRC

\documentclass[ALICE,manyauthors]{cernphprep}
\usepackage[comma,square,numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{url,color}
\usepackage{enumerate}   
%\usepackage{refcheck}
\linenumbers

@@

 % off by redefinding RHNOTE
\newcommand{\RHNOTE}[1]{{\bf RH:  #1}} 
\renewcommand{\RHNOTE}[1]{}  % switch off
\newcommand{\multfigsize}{0.95}
\begin{titlepage}
%
\PHyear{2017}
\PHnumber{xxx}                 % required, obtained from PH
\PHdate{21 August}              % required, will be obtained from PH
%
%
%%% Put your own title + short title here:
\title{Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\mathbf{\sqrt{s_{\rm NN}}}$ = 2.76 TeV}
\ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers

@@

%%%%%%%% acknowledgements
\newenvironment{acknowledgement}{\relax}{\relax}
\begin{acknowledgement}
\section*{Acknowledgements}
%\input{acknowledgements_jan2015.tex}    %%%%%%% get the lates version before submitting
\end{acknowledgement}
%
%
%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
%\bibliographystyle{apsrev4-1}   % Put here the style file name for the paper, i.e.apsrev4-1
%\bibliography{biblio}
%\input {bibliography.tex}  
%

%\nocite{*}

% \bibliographystyle{mybibstyle}
%\bibliographystyle{utphys}
%\bibliography{paper}
\bibliographystyle{utphys}
\bibliography{paper.bib}
\newpage
%
%\input{}               %%%%%%%%%%% put your appendices here
\input{appendix.tex}
%
%%%%%%%%% appendix with author list
\section{The ALICE Collaboration}
\label{app:collab}
%\input{Alice_Authorlist_2015-Feb-18.tex}  %%%%%%% done by webmaster team
%\input{}              %%%%%%%%%%%% put the references here
%
\end{document}

>>>>

\documentclass[ALICE,manyauthors]{cernphprep}
\pdfoutput=1
\usepackage[comma,square,numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{url,color}
\usepackage{enumerate}   
%\usepackage{refcheck}
%\linenumbers

@@

 % off by redefinding RHNOTE
\newcommand{\RHNOTE}[1]{{\bf RH:  #1}} 
\renewcommand{\RHNOTE}[1]{}  % switch off
\newcommand{\multfigsize}{0.95}
\begin{titlepage}
%
\PHyear{2017}
\PHnumber{215}                 % required, obtained from PH
\PHdate{21 August}              % required, will be obtained from PH
%
%
%%% Put your own title + short title here:
\title{Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\sqrt{s_{\rm NN}}$ = 2.76 TeV}
\ShortTitle{Correlations between different order flow harmonics}   % appears on right page headers

@@

%%%%%%%% acknowledgements
\newenvironment{acknowledgement}{\relax}{\relax}
\begin{acknowledgement}
\section*{Acknowledgements}
\input{fa_2017-08-29.tex}    %%%%%%% get the lates version before submitting
\end{acknowledgement}

\bibliographystyle{utphys}
\bibliography{paper.bib}
\newpage
%
%\input{}               %%%%%%%%%%% put your appendices here
\input{appendix.tex}
%
%%%%%%%%% appendix with author list
\section{The ALICE Collaboration}
\label{app:collab}
\input{Alice_Authorlist_2017-Aug-21.tex}  %%%%%%% done by webmaster team
%\input{}              %%%%%%%%%%%% put the references here
%
\end{document}
